Between Brussels and Britain: Uncovering the driving forces of Brexit

### 2024-04-19 paper/paper.qmd
Modelsumary worked

library(tidyverse)
library(palmerpenguins)
library(knitr)
```

@@

@@

#summary_result <- summary(first_model)

coefficients <- coef(first_model)
# Extract variable names (excluding intercept)
variables <- names(coefficients)[-1]  # Exclude the intercept

# Extract coefficients (excluding intercept)
coefficients <- coefficients[-1]  # Exclude the intercept

# Create data frame
coefs_df <- data.frame(Party = variables, Coefficients = coefficients)

# Print the data frame
print(coefs_df)
```

@@

It is worth stating that the reference ctaegory variable here is Alliance Party of Northern Ireland (APNI), which has holds an anti-Brexit stance.

@@

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

@@

This paper lays the groundwork for a more detailed study into which parties played the strongest role in Brexit. With the dataset of speeches already avaiable, devising an Intrumental Variable Framework to determine party influence seems like a suitable way forward.

As previously discussed, since speech occurence may not be a robust proxy for disagreement, employing an Instrumental Variable strategy will get rid of the reverse causality concerns.

### Instrumental Variable

When studying the relationship between two variables, there is a concern of reverse causality. For example, if we were to study the impact on institutions on the GDP of a nation, our estimates would be biased since GDP could also affect and improve an institituion. To tackle this, an Instrumental Variable approach can be used.

For this to happen,

\newpage

# References

>>>>

library(tidyverse)
library(knitr)
library(modelsummary)
```

@@

The entire paper uses R [@citeR]. The **tidyverse** package is used for data manipulation [@citetidyverse] and kableExtra for table formatting [@citekableExtra]

@@

modelsummary(
  list(
    "Log likelihood of EU discussion" = first_model)
)
```

@@

It is worth stating that the reference category variable here is Alliance Party of Northern Ireland (APNI), which has holds an anti-Brexit stance.

@@

## Disagreement and discourse - a relationship

While this paper studies a very specific question, the strategy used to model has implications that may be more far reaching than one would anticipate at face value. The strategy is simple - the more strong the disagreement, the more it is voiced in an environment conducive to that sort of discussion. This means it could have implications not only for the EU, but for studies that have nothing to do with socioeconomic outcomes.

For example, there exist many small institutions that are not usually at the center of statistical models, like a high school council. However, if there is a key issue up for discussion, it seems safe conjecture that students who disagree with actions of the school are more likely to voice their concerns, even repeatedly. This easy-to-miss behavioural strategy can be extrapolated to other important areas to enable or bolster a study.

@@

This paper lays the groundwork for a more detailed study into which parties played the strongest role in Brexit. With the dataset of speeches already available, devising an Intrumental Variable Framework to determine party influence seems like a suitable way forward.

When studying the relationship between two variables, there is a concern of reverse causality. For example, if we were to study the impact on institutions on the GDP of a nation, our estimates would be biased since GDP could also affect and improve an institution. To tackle this, an Instrumental Variable approach can be used.

In this setting, to help predict influence on brexit, we can use frequency of EU in speeches as the instrument. While this will require further testing and OLS regression to prove that frequency of EU speeches are correlated with supporting Brexit, as well as discussions about the Exclusion Restriction. However, those are beyond the scope of this course.

\newpage
# Appendix - Shiny application
# References
